An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
Four tasks

The sugarbag package provides a new method to implement hexagon tilegrams. 
Extending the tilegram to Australian applications required preserving the spatial relationships. It emphasises the capital cities as population hubs, and recognises the distances between locations of populations distributed across the large rural areas.

@@

There are four necessary tasks to create a hexagon tilegram.
These steps can be executed by the main function, `create_hexmap`, or can be applied separately for more flexibility.

They perform the following tasks:
 - Create the set of centroids to allocate
 - Create the set of hexagons to use
 - Allocate each centroid to an available hexagon
 - Transform the data for plotting

```{r tasks, eval = FALSE}
tibble::tibble(
  Step = c("1", "2", "3", "4"),
  Task = c("Create the set of centroids to allocate",
    "Create the set of hexagons to use", 
    "Allocate each centroid to an available hexagon",
    "Transform the data for plotting"),
  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
  Input = 
    c("1", "2", "3",
    "Allocated hexagons, identifying column, size of hexagons"),
  Output = c("1", "2", "3", "Fortified data frame")
  )
```

There are parameters used in the process that may be provided, or will be automatically derived.

### Use the sugarbag package

@@

### Example data

The polygon set of Local Government Areas of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used.

The longitude and latitude centre of the capital cities of Australia are used to  allocate areas around the closest capital city.

@@

**The following parameters will be determined within `create_hexmap` if not provided. They are created throughout the following example:**

@@

## Hexagon grid

@@

## Allocation of centroids

>>>>

The \CRANpkg{sugarbag} package provides a new method to implement hexagon tilegrams. 
Extending the tilegram to Australian applications required preserving the spatial relationships. It emphasises the capital cities as population hubs, and recognises the distances between locations of populations distributed across the large rural areas.

@@

There are four tasks to create a hexagon tilegram.
These steps can be executed by the main function, `create_hexmap`, or can be applied separately for more flexibility.

 1. Create the set of centroids to allocate
 2. Create the set of hexagons to use
 3. Allocate each centroid to an available hexagon
 4. Transform the data for plotting

There are parameters used in the process that can be provided, if they are not, they will be automatically derived.

### Install sugarbag package

@@

### Tasmania example

The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
A single column of the data set must be used to identify the unique areas. 
In this case, the unique LGA codes associated with each LGA have been used.

The longitude and latitude centre of the capital cities of Australia are used to  allocate areas around the closest capital city, as this example uses only the areas in the state of Tasmania, Hobart will be the common focal point.

@@

**The following parameters will be determined within `create_hexmap` if they are not provided. They are created throughout the following example:**

@@

## Create the hexagon grid points

@@

## Allocate each centroids to a hexagon grid point

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
Four tasks

There are four necessary tasks to create a hexagon tilegram. These steps
can be executed by the main function, \texttt{create\_hexmap}, or can be
applied separately for more flexibility.

They perform the following tasks: - Create the set of centroids to
allocate - Create the set of hexagons to use - Allocate each centroid to
an available hexagon - Transform the data for plotting

\begin{Schunk}
\begin{Sinput}
tibble::tibble(
  Step = c("1", "2", "3", "4"),
  Task = c("Create the set of centroids to allocate",
    "Create the set of hexagons to use", 
    "Allocate each centroid to an available hexagon",
    "Transform the data for plotting"),
  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
  Input = 
    c("1", "2", "3",
    "Allocated hexagons, identifying column, size of hexagons"),
  Output = c("1", "2", "3", "Fortified data frame")
  )
\end{Sinput}
\end{Schunk}

There are parameters used in the process that may be provided, or will
be automatically derived.

\hypertarget{use-the-sugarbag-package}{%
\subsubsection{Use the sugarbag
package}\label{use-the-sugarbag-package}}

@@

\hypertarget{example-data}{%
\subsubsection{Example data}\label{example-data}}

The polygon set of Local Government Areas of Tasmania in 2016 is
provided with the \CRANpkg{sugarbag} package as \texttt{tas\_lga}. A
single column of the data set must be used as a unique identifier of
areas. In this case, the unique LGA codes associated with each LGA have
been used.

The longitude and latitude centre of the capital cities of Australia are
used to allocate areas around the closest capital city.

>>>>

There are four tasks to create a hexagon tilegram. These steps can be
executed by the main function, \texttt{create\_hexmap}, or can be
applied separately for more flexibility.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Create the set of centroids to allocate
\item
  Create the set of hexagons to use
\item
  Allocate each centroid to an available hexagon
\item
  Transform the data for plotting
\end{enumerate}

There are parameters used in the process that can be provided, if they
are not, they will be automatically derived.

\hypertarget{install-sugarbag-package}{%
\subsubsection{Install sugarbag
package}\label{install-sugarbag-package}}

@@

\hypertarget{tasmania-example}{%
\subsubsection{Tasmania example}\label{tasmania-example}}

The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is
provided with the \CRANpkg{sugarbag} package as \texttt{tas\_lga}. A
single column of the data set must be used to identify the unique areas.
In this case, the unique LGA codes associated with each LGA have been
used.

The longitude and latitude centre of the capital cities of Australia are
used to allocate areas around the closest capital city, as this example
uses only the areas in the state of Tasmania, Hobart will be the common
focal point.
